What really matters (and to whom): Investigating heterogeneous effects in high-dimensional conjoint analyses

### 2024-11-28 Manuscript files/Manuscript.qmd
Tables attributes and covs

---
title: "What really matters (and to whom): Investigating heterogeneous effects in high-dimensional conjoint analyses"
author:
  - name: Thomas Reiter
    email: t.reiter@psy.lmu.de
  - name: Philipp Sterner
    email: p.sterner@psy.lmu.de
format: pdf
floatsintext: yes
editor_options: 
  markdown: 
    wrap: sentence
---

@@

# Method
Data of the above conjoint experiment was modeled by the previously described cjbart approach.
For this, we used the R package *cjbart* described in CITE.
We fitted a BART model containing the profile attributes and various subject-level covariates: age, country, gender, and political orientation, and subjects' agreement on different statements regarding political statements (e.g., EXAMPLE).
A list of all covariates, including their type, can be found in TABLE.
This resulted in a trained BART model that was used to make the (counterfactual) predictions needed for calculating the quantities of interest, such as IMCEs or AMCEs.

```{r covariates, echo=FALSE}
#| output: asis
library(kableExtra)

>>>>

---
title: "What really matters (and to whom): Investigating heterogeneous effects in high-dimensional conjoint analyses"
author:
  - name: Thomas Reiter
    email: t.reiter@psy.lmu.de
  - name: Philipp Sterner
    email: p.sterner@psy.lmu.de
format: pdf
pdf-engine: xelatex
header-includes:
  - \usepackage{array}
  - \usepackage{ragged2e}
  - \setlength{\extrarowheight}{2pt}
  - \renewcommand{\arraystretch}{1.5}  # Adjust row spacing
floatsintext: yes
editor_options: 
  markdown: 
    wrap: sentence
---

@@

# Method
Data of the above conjoint experiment was modeled by the previously described cjbart approach.
For this, we used the R package *cjbart* described in CITE.
We fitted a BART model containing the profile attributes and various subject-level covariates: age, country, gender, and political orientation, and subjects' agreement on different statements regarding political statements (e.g., EXAMPLE).
A list of all covariates, including their type, can be found in @tbl-covariates.
This resulted in a trained BART model that was used to make the (counterfactual) predictions needed for calculating the quantities of interest, such as IMCEs or AMCEs.

```{r covariates, echo=FALSE}
#| echo: false
#| results: asis
#| label: tbl-covariates

library(knitr)
library(kableExtra)

covs <- data.frame(
  Covariates = c(
    "Country",
    "Age",
    "Gender",
    "Political Orientation",
    "The political agenda should focus <br> on the war against Ukraine.",
    "How scared are you by the <br> Russian war against Ukraine?",
    "Does military support of [country] matter <br> regarding your current voting intention?",
    "The US-American imperialism is <br> the real threat to world peace.",
    "I can see why Russia feels <br> threatened by the West.",
    "Would you say that your general opinion <br> of the NATO is very positive, slightly positive, neither positive nor negative, slightly negative, or very negative?",
    "Ukraine should waive a NATO <br> membership if this would bring peace.",
    "Ukraine should not make <br> any cessions to achieve peace.",
    "Trading or deliveries of weapons <br> between countries should be prohibited.",
    "If a country is being attacked and <br> the aggressor is targeting civilians, <br> [country] should provide military support.",
    "If a country is being attacked and <br> the aggressor is targeting critical <br> infrastructure (e.g., hospitals or electricity <br> and water supply), [country] should provide military support.",
    "If a country is being attacked (without <br> actual fault) and the aggressor is taking <br> away its land, [country] should provide <br> military support."
  ),
  Scale_level = c(
    "Categorical with 5 levels: <br> Germany, UK, USA, France, Italy",
    "Continuous",
    "Categorical with 2 levels: <br> male and female",
    "Categorical with 3 levels: <br> left, middle, right",
    "Categorical: 6-point Likert scale",
    "Categorical: 7-point Likert scale <br> (<em>not scared at all</em> to <em>very scared</em>)",
    "Categorical: 4-point Likert scale <br> (<em>matters a lot</em> to <em>does not matter at all</em>)",
    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
    "Categorical: 5-point Likert scale <br> (<em>very positive</em> to <em>very negative</em>)",
    "Categorical with 2 levels: yes and no",
    "Categorical with 2 levels: yes and no",
    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)"
  )
)

knitr::kable(covs, 
             format = "html", 
             col.names = c("Covariates", "Scale Level"), 
             escape = FALSE,
             caption = "Covariates and corresponding scale levels used in the analyses.")
